Are rankings of financial analysts useful to investors?

### 2015-03-16 doc/paper/paper-knitr-APS.Rnw
some changes

\bibliographystyle{ecta}
%\bibliographystyle{newapa}
\bibliography{rank}

@@

dimnames(bl.results)[[1]] <- c('\\textit{CONS}','\\textit{TP}','\\textit{EPS}','\\textit{Market}')
results.final <- bl.results[4,1,]
cat(paste(c('Strategy','Annualized return (in \\%)','Annualized Std. dev (in \\%)','Sharpe ratio' ,'Average num. stock','Average turnover rate'), collapse = "&"),'\\\\')
#cat('\\multicolumn{5}{l}{\\textbf{Panel A: Market}} \n')
print(xtable(t(data.table('\\textit{Market}'=results.final)),display=c('s','f','f','f','d','f'),digits=3,align=c('r',rep('c',length(results.final)))),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0),command=c('\\multicolumn{5}{l}{\\textbf{Panel A}} \\\\ \n')),sanitize.text.function = function(x) x)
cat('\\midrule \n')
@
\end{tabularx}

\begin{tabularx}{\linewidth}{r*{5}{Y}}
  \multicolumn{5}{l}{\textbf{Panel B: \tr{} }} \\
<<bl-nr,echo=F,results='asis'>>=
print(xtable(bl.results[1:3,1,],display=c('s','f','f','f','d','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(nrow(bl.results[1:3,1,])),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
@
\end{tabularx}

\begin{tabularx}{\linewidth}{r*{5}{Y}}
  \multicolumn{5}{l}{\textbf{Panel C: \naive{}}} \\
<<bl-pt,echo=F,results='asis'>>=
print(xtable(bl.results[1:3,2,],display=c('s','f','f','f','d','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),,add.to.row=list(pos=list(nrow(bl.results[1:3,2,])),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
@
\end{tabularx}
\begin{tabularx}{\linewidth}{r*{5}{Y}}
  \multicolumn{5}{l}{\textbf{Panel D: \default{}}} \\
<<bl-eps,echo=F,results='asis'>>=
print(xtable(bl.results[1:3,3,],display=c('s','f','f','f','d','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),sanitize.text.function = function(x) x)
@
\bottomrule
\end{tabularx}
\end{table}

@@

print(xtable(acast(melt(periods.array[,c(4,1,2,3),1,'yes',c(1,4)]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{9}{l}{\\textbf{Panel A: \\tr{}}} \\\\\n', '\\midrule \n')))

@@

print(xtable(acast(melt(periods.array[,c(4,1,2,3),2,'yes',c(1,4)]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{9}{l}{\\textbf{Panel B: \\naive{}}} \\\\\n', '\\midrule \n')))

@@

print(xtable(acast(melt(periods.array[,c(4,1,2,3),3,'yes',c(1,4)]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{5}{l}{\\textbf{Panel C: \\default{}}} \\\\\n','\\midrule \n')))
@
\bottomrule
\end{tabular}}
\end{table}

>>>>

\bibliographystyle{chicago}
%\bibliographystyle{newapa}
\bibliography{rank}

@@

dimnames(bl.results)[[1]] <- c('\\textit{CONS}','\\textit{TP}','\\textit{EPS}','\\textit{Market}')
results.final <- bl.results[4,1,]
cat(paste(c('Strategy','Annualized return (in \\%)','Annualized Std. dev (in \\%)','Sharpe ratio' ,'Average num. stock','Average turnover rate'), collapse = "&"),'\\\\')
#cat('\\multicolumn{5}{l}{\\textbf{Panel A: Market}} \n')
print(xtable(t(data.table('\\textit{Market}'=results.final)),display=c('s','f','f','f','d','f'),digits=4,align=c('r',rep('c',length(results.final)))),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0),command=c('\\multicolumn{5}{l}{\\textbf{Panel A}} \\\\ \n')),sanitize.text.function = function(x) x)
cat('\\midrule \n')
@
\end{tabularx}

\begin{tabularx}{\linewidth}{r*{5}{Y}}
  \multicolumn{5}{l}{\textbf{Panel B: \tr{} }} \\
<<bl-nr,echo=F,results='asis'>>=
print(xtable(bl.results[1:3,1,],display=c('s','f','f','f','d','f'),digits=4),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(nrow(bl.results[1:3,1,])),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
@
\end{tabularx}

\begin{tabularx}{\linewidth}{r*{5}{Y}}
  \multicolumn{5}{l}{\textbf{Panel C: \naive{}}} \\
<<bl-pt,echo=F,results='asis'>>=
print(xtable(bl.results[1:3,2,],display=c('s','f','f','f','d','f'),digits=4),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),,add.to.row=list(pos=list(nrow(bl.results[1:3,2,])),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
@
\end{tabularx}
\begin{tabularx}{\linewidth}{r*{5}{Y}}
  \multicolumn{5}{l}{\textbf{Panel D: \default{}}} \\
<<bl-eps,echo=F,results='asis'>>=
print(xtable(bl.results[1:3,3,],display=c('s','f','f','f','d','f'),digits=4),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),sanitize.text.function = function(x) x)
@
\bottomrule
\end{tabularx}
\end{table}

@@

print(xtable(acast(melt(periods.array[,c(4,1,2,3),1,'yes',c(1,4)]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=4),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{9}{l}{\\textbf{Panel A: \\tr{}}} \\\\\n', '\\midrule \n')))

@@

print(xtable(acast(melt(periods.array[,c(4,1,2,3),2,'yes',c(1,4)]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=4),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{9}{l}{\\textbf{Panel B: \\naive{}}} \\\\\n', '\\midrule \n')))

@@

print(xtable(acast(melt(periods.array[,c(4,1,2,3),3,'yes',c(1,4)]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=4),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{5}{l}{\\textbf{Panel C: \\default{}}} \\\\\n','\\midrule \n')))
@
\bottomrule
\end{tabular}}
\end{table}

### 2015-03-16 doc/paper/paper-knitr-APS.tex
some changes

Table (\ref{tab:rank-stat}) shows a contingency analysis of the ranks. 
%Chi square statistics include/ expected frequiency test
%Journ. of Fin economics 
Panel A shows the dynamics of each tercile for rankings based on target price  accuracy. We observe that analysts exhibit strong ranking consistency as, on average, they stay at the same tercile after one quarter. Of the top (bottom) most accurate (inaccurate) analysts in the previous quarter 67.769\% (69.548\%) remain in that same tercile after one quarter. After one year the corresponding figures are lower respectively 46.199\% and 41.09\% for the top and bottom terciles.

@@

Panel A show the statistics for the consensus expectations as defined in eq. (\ref{consq}). The average consensus among the analysts on stock expected returns in the  \tr{}, \naive{} and \default{} information sets are, respectively, 18.944\%, 18.99\%, and 22.207\% respectively. Panel B of the table shows the TP accuracy weighted average expected returns (16.068\%, 16.095\%, and 19.343\%). Panel C shows the EPS based weighted expected returns averages (14.964\%, 14.967\%, and 19.511\%).

@@

 &$top$ & 67.8 & 22.0 & 10.2 & 100.0 \\ 
  &$middle$ & 29.9 & 48.2 & 22.0 & 100.0 \\ 
  &$bottom$ & 13.4 & 17.1 & 69.5 & 100.0 \\ 
    &&\multicolumn{4}{c}{$t+4$}\\ 
&$top$ & 46.2 & 28.0 & 25.8 & 100.0 \\ 
  &$middle$ & 39.2 & 29.2 & 31.7 & 100.0 \\ 
  &$bottom$ & 32.1 & 26.8 & 41.1 & 100.0 \\

@@

\begin{tabularx}{\linewidth}{r*{4}{Y}}
\toprule
& Mean (in \%) & Median (in \%) &Std.dev\\
\midrule
  \multicolumn{4}{l}{\textbf{Panel A: Consensus}} \\ 
 \midrule 
\tr{} & 18.944 & 17.156 & 0.119 \\ 
  \naive{} & 18.990 & 17.173 & 0.119 \\ 
  \default{} & 22.207 & 20.707 & 0.101 \\

@@

  \end{tabularx}
  \begin{tabularx}{\linewidth}{r*{4}{Y}}
  \multicolumn{4}{l}{\textbf{Panel C: EPS}} \\ 
 \midrule 
\tr{} & 16.068 & 14.522 & 0.098 \\ 
  \naive{} & 16.095 & 14.525 & 0.098 \\ 
  \default{} & 19.343 & 18.179 & 0.084 \\

@@

\begin{table}[hp]
  \caption{Number of active stocks}
  \label{tab:stocks}
\ This table shows number of active stocks in each of the trading strategies conditional on different information sets: \tr{} (panel A), \naive{} (panel B) and \default{} (panel C). 
\begin{tabularx}{\linewidth}{r*{4}{Y}}
\toprule
Year& \textit{CONS}& \textit{TP} & \textit{EPS}\\
  \multicolumn{4}{l}{\textbf{Panel A: \tr{}}} \\ 
 \midrule 
1999 &  202 &  202 &  145 \\ 
  2000 &  269 &  269 &  211 \\ 
  2001 &  306 &  306 &  257 \\ 
  2002 &  333 &  333 &  299 \\ 
  2003 &  346 &  346 &  311 \\ 
  2004 &  351 &  351 &  331 \\ 
  2005 &  359 &  359 &  343 \\ 
  2006 &  361 &  361 &  344 \\ 
  2007 &  365 &  365 &  357 \\ 
  2008 &  361 &  361 &  339 \\ 
  2009 &  323 &  323 &  300 \\ 
   \midrule 
Total &  379 &  379 &  376 \\

\end{tabularx}
\begin{tabularx}{\linewidth}{r*{4}{Y}}
  \multicolumn{4}{l}{\textbf{Panel B: \naive{}}} \\ 
 \midrule 
1999 &   69 &   69 &   44 \\ 
  2000 &  235 &  235 &  186 \\ 
  2001 &  281 &  281 &  247 \\ 
  2002 &  323 &  323 &  288 \\ 
  2003 &  334 &  334 &  307 \\ 
  2004 &  341 &  341 &  318 \\ 
  2005 &  352 &  352 &  337 \\ 
  2006 &  359 &  359 &  343 \\ 
  2007 &  362 &  362 &  352 \\ 
  2008 &  361 &  361 &  349 \\ 
  2009 &  351 &  351 &  321 \\ 
   \midrule 
Total &  379 &  379 &  376 \\

\end{tabularx}
\begin{tabularx}{\linewidth}{r*{4}{Y}}
  \multicolumn{4}{l}{\textbf{Panel C: \default{}}} \\ 
 \midrule 
1999 &   69 &   69 &   54 \\ 
  2000 &  235 &  235 &  205 \\ 
  2001 &  284 &  284 &  264 \\ 
  2002 &  327 &  327 &  308 \\ 
  2003 &  341 &  341 &  326 \\ 
  2004 &  350 &  350 &  339 \\ 
  2005 &  364 &  364 &  357 \\ 
  2006 &  371 &  371 &  365 \\ 
  2007 &  375 &  375 &  371 \\ 
  2008 &  377 &  377 &  375 \\ 
  2009 &  379 &  379 &  378 \\ 
   \midrule 
Total &  379 &  379 &  378 \\

@@

\begin{tabularx}{\linewidth}{r*{5}{Y}}
  \toprule
  %\multicolumn{5}{l}{\textbf{Panel A: Market}} \\
Strategy&Annualized return (in \%)&Annualized Std. dev (in \%)&Sharpe ratio&Average num. stock&Average turnover rate \\  \multicolumn{5}{l}{\textbf{Panel A}} \\ 
\textit{Market} & -3.032 & 16.654 & -0.182 &  499 & 0.053 \\ 
  \midrule

@@

\begin{tabularx}{\linewidth}{r*{5}{Y}}
  \multicolumn{5}{l}{\textbf{Panel B: \tr{} }} \\
 \textit{CONS} & 2.247 & 15.032 & 0.149 &  257 & 0.277 \\ 
  \textit{TP} & 5.400 & 14.552 & 0.371 &  257 & 0.298 \\ 
  \textit{EPS} & 1.957 & 15.145 & 0.129 &  209 & 0.501 \\ 
   \midrule

@@

\begin{tabularx}{\linewidth}{r*{5}{Y}}
  \multicolumn{5}{l}{\textbf{Panel C: \naive{}}} \\
 \textit{CONS} & 0.449 & 15.993 & 0.028 &  252 & 0.250 \\ 
  \textit{TP} & 0.622 & 15.682 & 0.040 &  252 & 0.256 \\ 
  \textit{EPS} & -0.361 & 16.100 & -0.022 &  206 & 0.408 \\ 
   \midrule

\end{tabularx}
\begin{tabularx}{\linewidth}{r*{5}{Y}}
  \multicolumn{5}{l}{\textbf{Panel D: \default{}}} \\
 \textit{CONS} & 0.413 & 15.873 & 0.026 &  257 & 0.185 \\ 
  \textit{TP} & 0.441 & 15.658 & 0.028 &  257 & 0.189 \\ 
  \textit{EPS} & 0.441 & 15.702 & 0.028 &  250 & 0.198 \\

@@

  \multicolumn{9}{l}{\textbf{Panel A: \tr{}}} \\
2000Q1/2004Q4 & -3.401 & -0.201 & 5.269 & 0.343 & 7.564 & 0.509 & 3.757 & 0.245 \\ 
  2001Q1/2005Q4 & -1.539 & -0.093 & 4.232 & 0.280 & 7.159 & 0.496 & 4.859 & 0.335 \\ 
  2002Q1/2006Q4 & 2.567 & 0.196 & 6.230 & 0.504 & 9.682 & 0.816 & 6.428 & 0.537 \\ 
  2003Q1/2007Q4 & 7.919 & 0.925 & 10.092 & 1.180 & 14.339 & 1.817 & 10.708 & 1.296 \\ 
  2004Q1/2008Q4 & -5.667 & -0.435 & -3.059 & -0.245 & 1.285 & 0.103 & -2.163 & -0.174 \\ 
  2005Q1/2009Q4 & -2.662 & -0.158 & -0.689 & -0.046 & 3.279 & 0.225 & 0.187 & 0.012 \\ 
   \midrule 
All period & -3.032 & -0.182 & 2.247 & 0.149 & 5.400 & 0.371 & 1.957 & 0.129 \\

@@

\resizebox{\textwidth}{!}{%
\begin{tabular}{rrrrrrrrr}
%\begin{tabularx}{\linewidth}{r*{9}{Y}}
  \multicolumn{9}{l}{\textbf{Panel B: \naive{}}} \\
2000Q1/2004Q4 & -3.401 & -0.201 & 3.401 & 0.215 & 3.345 & 0.217 & 1.045 & 0.066 \\ 
  2001Q1/2005Q4 & -1.539 & -0.093 & 2.840 & 0.180 & 3.538 & 0.232 & 2.537 & 0.163 \\ 
  2002Q1/2006Q4 & 2.567 & 0.196 & 5.837 & 0.468 & 6.229 & 0.517 & 5.415 & 0.448 \\ 
  2003Q1/2007Q4 & 7.919 & 0.925 & 9.410 & 1.098 & 9.965 & 1.242 & 9.298 & 1.149 \\ 
  2004Q1/2008Q4 & -5.667 & -0.435 & -4.826 & -0.349 & -4.254 & -0.311 & -4.551 & -0.333 \\ 
  2005Q1/2009Q4 & -2.662 & -0.158 & -2.419 & -0.147 & -2.029 & -0.125 & -1.748 & -0.105 \\ 
   \midrule 
All period & -3.032 & -0.182 & 0.449 & 0.028 & 0.622 & 0.040 & -0.361 & -0.022 \\

\midrule
\end{tabular}}
\resizebox{\textwidth}{!}{%
\begin{tabular}{rrrrrrrrr}
%\begin{tabularx}{\linewidth}{r*{9}{Y}}
  \multicolumn{5}{l}{\textbf{Panel C: \default{}}} \\
2000Q1/2004Q4 & -3.401 & -0.201 & 4.702 & 0.305 & 4.367 & 0.291 & 4.204 & 0.277 \\ 
  2001Q1/2005Q4 & -1.539 & -0.093 & 3.873 & 0.253 & 4.112 & 0.278 & 4.294 & 0.286 \\ 
  2002Q1/2006Q4 & 2.567 & 0.196 & 5.774 & 0.455 & 6.045 & 0.494 & 5.997 & 0.491 \\ 
  2003Q1/2007Q4 & 7.919 & 0.925 & 8.344 & 0.881 & 8.584 & 0.964 & 8.604 & 0.972 \\ 
  2004Q1/2008Q4 & -5.667 & -0.435 & -6.018 & -0.432 & -5.686 & -0.412 & -5.537 & -0.402 \\ 
  2005Q1/2009Q4 & -2.662 & -0.158 & -3.700 & -0.225 & -3.337 & -0.203 & -3.186 & -0.194 \\ 
   \midrule 
All period & -3.032 & -0.182 & 0.413 & 0.026 & 0.441 & 0.028 & 0.441 & 0.028 \\

>>>>

Table (\ref{tab:rank-stat}) shows a contingency analysis of the ranks. 
%Chi square statistics include/ expected frequiency test
%Journ. of Fin economics 
Panel A shows the dynamics of each tercile for rankings based on target price  accuracy. We observe that analysts exhibit strong ranking consistency as, on average, they stay at the same tercile after one quarter. Of the top (bottom) most accurate (inaccurate) analysts in the previous quarter 67.739\% (69.582\%) remain in that same tercile after one quarter. After one year the corresponding figures are lower respectively 46.189\% and 41.204\% for the top and bottom terciles.

@@

Panel A show the statistics for the consensus expectations as defined in eq. (\ref{consq}). The average consensus among the analysts on stock expected returns in the  \tr{}, \naive{} and \default{} information sets are, respectively, 18.947\%, 18.993\%, and 22.216\% respectively. Panel B of the table shows the TP accuracy weighted average expected returns (16.071\%, 16.098\%, and 19.352\%). Panel C shows the EPS based weighted expected returns averages (14.964\%, 14.967\%, and 19.511\%).

@@

 &$top$ & 67.7 & 22.1 & 10.2 & 100.0 \\ 
  &$middle$ & 29.9 & 48.2 & 21.9 & 100.0 \\ 
  &$bottom$ & 13.4 & 17.1 & 69.6 & 100.0 \\ 
    &&\multicolumn{4}{c}{$t+4$}\\ 
&$top$ & 46.2 & 28.0 & 25.8 & 100.0 \\ 
  &$middle$ & 39.2 & 29.2 & 31.6 & 100.0 \\ 
  &$bottom$ & 32.1 & 26.7 & 41.2 & 100.0 \\

@@

\begin{tabularx}{\linewidth}{r*{4}{Y}}
\toprule
& Mean (in \%) & Median (in \%) &Std.dev\\
\midrule
  \multicolumn{4}{l}{\textbf{Panel A: Consensus}} \\ 
 \midrule 
\tr{} & 18.947 & 17.156 & 0.119 \\ 
  \naive{} & 18.993 & 17.173 & 0.119 \\ 
  \default{} & 22.216 & 20.715 & 0.101 \\

@@

  \end{tabularx}
  \begin{tabularx}{\linewidth}{r*{4}{Y}}
  \multicolumn{4}{l}{\textbf{Panel C: EPS}} \\ 
 \midrule 
\tr{} & 16.071 & 14.525 & 0.098 \\ 
  \naive{} & 16.098 & 14.528 & 0.098 \\ 
  \default{} & 19.352 & 18.195 & 0.084 \\

@@

\begin{table}[hp]
  \caption{Number of active stocks}
  \label{tab:stocks}
\ This table shows number of active stocks in each of the trading strategies conditional on different information sets: \tr{} (panel A), \naive{} (panel B) and \default{} (panel C). 
\begin{tabularx}{\linewidth}{r*{4}{Y}}
\toprule
Year& \textit{CONS}& \textit{TP} & \textit{EPS}\\
  \multicolumn{4}{l}{\textbf{Panel A: \tr{}}} \\ 
 \midrule 
1999 &  202 &  202 &  145 \\ 
  2000 &  269 &  269 &  211 \\ 
  2001 &  306 &  306 &  257 \\ 
  2002 &  333 &  333 &  299 \\ 
  2003 &  346 &  346 &  311 \\ 
  2004 &  351 &  351 &  331 \\ 
  2005 &  358 &  358 &  343 \\ 
  2006 &  360 &  360 &  344 \\ 
  2007 &  364 &  364 &  357 \\ 
  2008 &  360 &  360 &  339 \\ 
  2009 &  323 &  323 &  300 \\ 
   \midrule 
Total &  378 &  378 &  376 \\

\end{tabularx}
\begin{tabularx}{\linewidth}{r*{4}{Y}}
  \multicolumn{4}{l}{\textbf{Panel B: \naive{}}} \\ 
 \midrule 
1999 &   69 &   69 &   44 \\ 
  2000 &  235 &  235 &  186 \\ 
  2001 &  281 &  281 &  247 \\ 
  2002 &  323 &  323 &  288 \\ 
  2003 &  334 &  334 &  307 \\ 
  2004 &  341 &  341 &  318 \\ 
  2005 &  352 &  352 &  337 \\ 
  2006 &  358 &  358 &  343 \\ 
  2007 &  361 &  361 &  352 \\ 
  2008 &  360 &  360 &  349 \\ 
  2009 &  351 &  351 &  321 \\ 
   \midrule 
Total &  378 &  378 &  376 \\

\end{tabularx}
\begin{tabularx}{\linewidth}{r*{4}{Y}}
  \multicolumn{4}{l}{\textbf{Panel C: \default{}}} \\ 
 \midrule 
1999 &   69 &   69 &   54 \\ 
  2000 &  235 &  235 &  205 \\ 
  2001 &  284 &  284 &  264 \\ 
  2002 &  327 &  327 &  308 \\ 
  2003 &  341 &  341 &  326 \\ 
  2004 &  350 &  350 &  339 \\ 
  2005 &  364 &  364 &  357 \\ 
  2006 &  370 &  370 &  365 \\ 
  2007 &  374 &  374 &  371 \\ 
  2008 &  376 &  376 &  375 \\ 
  2009 &  378 &  378 &  378 \\ 
   \midrule 
Total &  378 &  378 &  378 \\

@@

\begin{tabularx}{\linewidth}{r*{5}{Y}}
  \toprule
  %\multicolumn{5}{l}{\textbf{Panel A: Market}} \\
Strategy&Annualized return (in \%)&Annualized Std. dev (in \%)&Sharpe ratio&Average num. stock&Average turnover rate \\  \multicolumn{5}{l}{\textbf{Panel A}} \\ 
\textit{Market} & -3.0323 & 16.6545 & -0.1821 &   499 & 0.0526 \\ 
  \midrule

@@

\begin{tabularx}{\linewidth}{r*{5}{Y}}
  \multicolumn{5}{l}{\textbf{Panel B: \tr{} }} \\
 \textit{CONS} & 2.2470 & 15.0316 & 0.1495 &   257 & 0.2774 \\ 
  \textit{TP} & 5.3998 & 14.5525 & 0.3711 &   257 & 0.2982 \\ 
  \textit{EPS} & 1.9567 & 15.1450 & 0.1292 &   209 & 0.5006 \\ 
   \midrule

@@

\begin{tabularx}{\linewidth}{r*{5}{Y}}
  \multicolumn{5}{l}{\textbf{Panel C: \naive{}}} \\
 \textit{CONS} & 0.4491 & 15.9932 & 0.0281 &   252 & 0.2503 \\ 
  \textit{TP} & 0.6217 & 15.6819 & 0.0396 &   252 & 0.2556 \\ 
  \textit{EPS} & -0.3614 & 16.1002 & -0.0224 &   206 & 0.4077 \\ 
   \midrule

\end{tabularx}
\begin{tabularx}{\linewidth}{r*{5}{Y}}
  \multicolumn{5}{l}{\textbf{Panel D: \default{}}} \\
 \textit{CONS} & 0.4128 & 15.8729 & 0.0260 &   257 & 0.1853 \\ 
  \textit{TP} & 0.4414 & 15.6585 & 0.0282 &   257 & 0.1888 \\ 
  \textit{EPS} & 0.4409 & 15.7018 & 0.0281 &   250 & 0.1977 \\

@@

  \multicolumn{9}{l}{\textbf{Panel A: \tr{}}} \\
2000Q1/2004Q4 & -3.4007 & -0.2011 & 5.2694 & 0.3428 & 7.5639 & 0.5094 & 3.7574 & 0.2453 \\ 
  2001Q1/2005Q4 & -1.5393 & -0.0926 & 4.2321 & 0.2804 & 7.1589 & 0.4958 & 4.8590 & 0.3349 \\ 
  2002Q1/2006Q4 & 2.5665 & 0.1960 & 6.2298 & 0.5039 & 9.6824 & 0.8158 & 6.4279 & 0.5371 \\ 
  2003Q1/2007Q4 & 7.9195 & 0.9254 & 10.0924 & 1.1796 & 14.3387 & 1.8166 & 10.7077 & 1.2962 \\ 
  2004Q1/2008Q4 & -5.6671 & -0.4354 & -3.0593 & -0.2447 & 1.2854 & 0.1032 & -2.1627 & -0.1744 \\ 
  2005Q1/2009Q4 & -2.6625 & -0.1582 & -0.6887 & -0.0461 & 3.2793 & 0.2252 & 0.1873 & 0.0122 \\ 
   \midrule 
All period & -3.0323 & -0.1821 & 2.2470 & 0.1495 & 5.3998 & 0.3711 & 1.9567 & 0.1292 \\

@@

\resizebox{\textwidth}{!}{%
\begin{tabular}{rrrrrrrrr}
%\begin{tabularx}{\linewidth}{r*{9}{Y}}
  \multicolumn{9}{l}{\textbf{Panel B: \naive{}}} \\
2000Q1/2004Q4 & -3.4007 & -0.2011 & 3.4013 & 0.2145 & 3.3446 & 0.2169 & 1.0450 & 0.0656 \\ 
  2001Q1/2005Q4 & -1.5393 & -0.0926 & 2.8396 & 0.1805 & 3.5380 & 0.2323 & 2.5370 & 0.1628 \\ 
  2002Q1/2006Q4 & 2.5665 & 0.1960 & 5.8368 & 0.4684 & 6.2288 & 0.5169 & 5.4148 & 0.4477 \\ 
  2003Q1/2007Q4 & 7.9195 & 0.9254 & 9.4104 & 1.0983 & 9.9651 & 1.2416 & 9.2980 & 1.1488 \\ 
  2004Q1/2008Q4 & -5.6671 & -0.4354 & -4.8255 & -0.3490 & -4.2537 & -0.3109 & -4.5513 & -0.3325 \\ 
  2005Q1/2009Q4 & -2.6625 & -0.1582 & -2.4189 & -0.1474 & -2.0293 & -0.1250 & -1.7483 & -0.1050 \\ 
   \midrule 
All period & -3.0323 & -0.1821 & 0.4491 & 0.0281 & 0.6217 & 0.0396 & -0.3614 & -0.0224 \\

\midrule
\end{tabular}}
\resizebox{\textwidth}{!}{%
\begin{tabular}{rrrrrrrrr}
%\begin{tabularx}{\linewidth}{r*{9}{Y}}
  \multicolumn{5}{l}{\textbf{Panel C: \default{}}} \\
2000Q1/2004Q4 & -3.4007 & -0.2011 & 4.7015 & 0.3048 & 4.3673 & 0.2913 & 4.2041 & 0.2771 \\ 
  2001Q1/2005Q4 & -1.5393 & -0.0926 & 3.8730 & 0.2529 & 4.1116 & 0.2777 & 4.2935 & 0.2865 \\ 
  2002Q1/2006Q4 & 2.5665 & 0.1960 & 5.7738 & 0.4555 & 6.0452 & 0.4941 & 5.9968 & 0.4914 \\ 
  2003Q1/2007Q4 & 7.9195 & 0.9254 & 8.3443 & 0.8812 & 8.5839 & 0.9635 & 8.6038 & 0.9724 \\ 
  2004Q1/2008Q4 & -5.6671 & -0.4354 & -6.0175 & -0.4319 & -5.6861 & -0.4116 & -5.5371 & -0.4018 \\ 
  2005Q1/2009Q4 & -2.6625 & -0.1582 & -3.7003 & -0.2250 & -3.3367 & -0.2025 & -3.1863 & -0.1942 \\ 
   \midrule 
All period & -3.0323 & -0.1821 & 0.4128 & 0.0260 & 0.4414 & 0.0282 & 0.4409 & 0.0281 \\
